Too many colors spoil the graph

### 2024-12-13 text/23/too-many-colors.rmd
Updated 23/too-many-colors

```{r too-many-colors-01, echo=FALSE, warning=FALSE}
library(usmap)
library(ggplot2)
plot_usmap(
    data = statepov, 
    values = "pct_pov_2014", 
    color = "red") -> us
us +
  scale_fill_continuous(
        low = "white", 
        high = "red", 
        name = "Poverty rate (2014)", 
        label = scales::comma) + 
  theme(legend.position = "right")
```

>>>>

```{r too-many-colors-01, echo=FALSE, warning=FALSE}
library(usmap)
library(ggplot2)
plot_usmap(
    data = statepov, 
    values = "pct_pov_2021", 
    color = "red") -> us
us +
  scale_fill_continuous(
        low = "white", 
        high = "red", 
        name = "Poverty rate (2021)", 
        label = scales::comma) + 
  theme(legend.position = "right")
```
